---
title: "412/612 Project Proposal"
author: "Anna Livingstone & Philip Eigen"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: "hide"
    toc: True
    toc_float: True
  pdf_document: default
---

# Intro
For this project, we are looking at how a number of variables affect sale price of a used car between individuals. The original data for this project can be found [here](https://www.kaggle.com/datasets/nehalbirla/vehicle-dataset-from-cardekho?select=car+details+v4.csv).

```{r message=F, warning=F}
library(tidyverse)
library(fastDummies)
data <- read.csv("cardetailsv4.csv")
```

# Data Cleaning
We have to do a few things to clean the data and extract the information we want. First we get rid of all NA values. Next, we select our variables. We will be using price (in dollars) as out response variable, and year, kilometers (on the car), engine (size in cc), seating capacity, fuel tank capacity (in liters), transmission (manual vs. automatic), drivetrain (FWD, RWD, & AWD), height (in mm), and width (in mm). Next, we must reformat Engine from a character vector presented with " cc" at the end to a numerical vector.

```{r}
data %>% 
  na.omit() %>% 
  filter(Seller.Type=="Individual", Engine!="", Drivetrain!="") %>% 
  select(Price, Year, Kilometer, Engine, Seating.Capacity, Fuel.Tank.Capacity, Transmission, Drivetrain, Height, Width) %>% 
  mutate(Engine=as.numeric(str_replace_all(Engine, "[ c]", "")))-> data2
```

# Formatting Data
Next, because we have two categorical variables which cannot be represented numerically, we must one-hot encode them. Those two variables are Transmission and Drivetrain. This process will automatically remove the existing Transmission and Drivetrain columns. In order to be able to calculate the regression, we will have to pick a baseline for each variable and remove it from our data. In our case, we will be setting automatic transmissions and front-wheel drive as our baselines, hence why we drop them with the subset function.
```{r}
data3 <- dummy_cols(.data=data2, select_columns=c("Transmission","Drivetrain"), remove_selected_columns=T)
data3 = subset(data3, select=-c(Transmission_Automatic, Drivetrain_FWD))
names(data3)
```
With all of our cleaning said and done, we can see our final columns above. Our final dataset has dimensions of `r dim(data3)`.

# Building a Model
Now we will build out model. It is a basic multiple linear regression.
```{r}
library(lbutils)
library(broom)
cm <- lm(data3, formula=Price~Year+Kilometer+Engine+Seating.Capacity+Fuel.Tank.Capacity+Height+Width+Transmission_Manual+Drivetrain_AWD+Drivetrain_RWD)
tidy(cm)
```

# Checking Residuals
This residual vs fitted values plot shows that there is a clear violation in our assumptions of constant variance of the residuals
```{r}
ggplot(cm, aes(x=cm$fitted.values, y=cm$residuals)) +
  geom_point()
```

# Adjusting Model
We will try using the log-transformed values of our response variable, price, and rebuild our model.
```{r}
tcm <- lm(data3, formula=log(Price)~Year+Kilometer+Engine+Seating.Capacity+Fuel.Tank.Capacity+Height+Width+Transmission_Manual+Drivetrain_AWD+Drivetrain_RWD)
tidy(tcm)
```

# Checking New Residuals
Here we can see a residual vs fitted values plot that does fit our assumptions. We will use this as our model.
```{r}
ggplot(tcm, aes(x=cm$fitted.values, y=tcm$residuals)) +
  geom_point()
```

# Checking VIF
Looking at this table of Variance Inflation Factors (VIF), we can see that we are not suffering from significant multicollinearity.
```{r}
olsrr::ols_vif_tol(tcm)
```

# Citations

FastDummies:
  Kaplan J (2020). _fastDummies: Fast Creation of Dummy (Binary) Columns and Rows from Categorical Variables_. R
  package version 1.6.3, <https://CRAN.R-project.org/package=fastDummies>.
  
Olsrr:
  Hebbali A (2020). _olsrr: Tools for Building OLS Regression Models_. R package version 0.5.3,
  <https://CRAN.R-project.org/package=olsrr>.
  
R:
  R Core Team (2022). R: A language and environment for statistical computing. R Foundation for Statistical
  Computing, Vienna, Austria. URL https://www.R-project.org/.
  
Tidyverse:
  Wickham H, Averick M, Bryan J, Chang W, McGowan LD, François R, Grolemund G, Hayes A, Henry L, Hester J, Kuhn M,
  Pedersen TL, Miller E, Bache SM, Müller K, Ooms J, Robinson D, Seidel DP, Spinu V, Takahashi K, Vaughan D, Wilke
  C, Woo K, Yutani H (2019). “Welcome to the tidyverse.” _Journal of Open Source Software_, *4*(43), 1686.
  doi:10.21105/joss.01686 <https://doi.org/10.21105/joss.01686>.